---
title: "Where?"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What we need here:

- tables under "Where?" tab
- omit heatmaps (these are in their own section)
- campus inclusiveness treemap
- emu inclusiveness treemap

## Brian's Code
```{r}

```

## Standardize
```{r}

```


## UI draft

## Server draft


## Possibly useful code


just droppped in some code below. this is just the outline and works when you load everything in as .RData, but we want to avoid that. but you can use as draft - anwesha

### Standardized piece (probably can be condensed even more)
```{r initial setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
library(reactable)
library(htmltools)
library(magick)
library(treemapify)
library(udpipe)
library(tidytext)
library(wordcloud2)
library(igraph)
library(ggraph)

ay_1<- 2122 #CHANGE year (academic year format 1920 etc.)
ay_2<- 2223 #CHANGE year (academic year format 1920 etc.)

#function for big Ns that have , marks
big_n<- function(x) {
  prettyNum(x, big.mark = ",", scientific = F)
}

#stats that get 1 decimal like percentages
stat_1<- function(x) {
  formatC(x, format = "f", digits = 1)
}

#get place names
places<- read_csv(
  paste0(
    "data/processed/pbb_eoy_1718_thru_",
    ay_1,
    "_places.csv"
  )
)

waves<- c("Spring 2022, Spring 2020, Spring 2019, Spring 2018") #CHANGE add waves as more data come in


#read data ####

#get long campus data
campus_long<- read_csv(
  paste0(
    "data/processed/pbb_eoy_1718_thru_",
    ay_1,
    "_campus_bdb_long.csv"
  )
) %>%
  left_join(
    .,
    places %>%
      filter(level == "campus"),
    by = c("ayear", "place")
  ) %>%
  within(cohort[is.na(cohort)]<- "no cohort") %>% #a trick to let me do the same function to data that are either cohort-specific or cohort-irrelevant
  within(
    full_place[
      full_place == "Thompsons"
    ]<- "Thompson's University Center"
  )

#get survey demos ####
#need to get gi and so from eoy when available, otherwise bl
#need to get others from bl data

#get recs demos ####
#need to add eoy22 who don't have bl to a set with bl

#combine above for doing analyses by demos ####
#join ds and dr to campus_long - reference bl wb by demos

#get emu long data
emu_long<- read_csv(
  paste0(
    "data/processed/pbb_eoy_1718_thru_",
    ay_1,
    "_emu_bdb_long.csv"
  )
) %>%
  left_join(
    .,
    places %>%
      filter(level == "emu"),
    by = c("ayear", "place")
  ) %>%
  within(cohort[is.na(cohort)]<- "no cohort") %>%
  filter(
    place_num %in% c("b1", "b2", "b3", "db1", "db2", "db3")
  ) %>%
  within(
    full_place[
      full_place == "Craft Center - Outdoor"
    ]<- "Craft Center"
  )

#compute n resps > 3 (method was split across 2 maps in 1718 and 1819. students were instructed to select 3 but some selected more)
too_many_resps_emu<- read_csv(
  paste0(
    "data/processed/pbb_eoy_1718_thru_",
    ay_1,
    "_emu_bdb_wide.csv"
  ),
  guess_max = 1900
) %>%
  filter(
    !is.na(b4) |
      !is.na(db4)
  ) %>%
  group_by(ayear) %>%
  summarise(n = sum(!is.na(id)))

#combine above for doing analyses by demos ####
#join ds and dr to emu_long - reference bl wb by demos


#function for getting place counts
place_fun<- function(dat, s_vec, c_vec, gt, lt, p, by_p, n_dat) {
  df<- full_join(
    dat  %>%
      within(
        full_place[
          agg_place == "Other" |
            agg_place == "Out of Bounds"
        ]<- "Other/Out of Bounds"
      ) %>%
      within(
        agg_place[
          agg_place == "Other" |
            agg_place == "Out of Bounds"
        ]<- "Other/Out of Bounds"
      ) %>%
      filter(
        sample %in% c(s_vec) &
          cohort %in% c(c_vec) &
          ayear > gt &
          ayear < lt &
          sent == "Belong"
      ) %>%
      count(!!sym(p)) %>%
      arrange(desc(n)),
    dat %>%
      within(
        full_place[
          agg_place == "Other" |
            agg_place == "Out of Bounds"
        ]<- "Other/Out of Bounds"
      ) %>%
      within(
        agg_place[
          agg_place == "Other" |
            agg_place == "Out of Bounds"
        ]<- "Other/Out of Bounds"
      ) %>%
      filter(
        sample %in% c(s_vec) &
          cohort %in% c(c_vec) &
          ayear > gt &
          ayear < lt &
          sent == "Don't Belong"
      ) %>%
      count(!!sym(p)) %>%
      arrange(desc(n)),
    by = by_p
  ) %>%
    filter(!!sym(p) != "No Place") %>%
    rename(
      n_b = n.x,
      n_db = n.y
    ) %>%
    within(n_b[is.na(n_b)]<- 0) %>%
    within(n_db[is.na(n_db)]<- 0) %>%
    mutate(
      perc_click_b = n_b/sum(n_b)*100,
      perc_click_db = n_db/sum(n_db)*100,
      perc_stud_b = n_b/sum(n_dat$n_b)*100,
      perc_stud_db = n_db/sum(n_dat$n_db)*100,
      incl = n_b/(n_b+n_db)*100
    ) %>%
    select(!!sym(p), incl, n_b, n_db, everything())
  return(df)
}

#lt term in ns_fun, nw_fun, and place_fun for us undergrad overall and us undergrad by cohort sets
lt_term<- 2223 #CHANGE increment term as ayears are added



#make vectors for indexing ####
vnm_long<- names(campus_long) #same as emu_long

cohorts<- c(
  "0102",
  "0708",
  "1011",
  "1112",
  "1415",
  "1516",
  "1617",
  "1718",
  "1819",
  "1920",
  "2021",
  "2122",
  "2223"
  #CHANGE add cohorts as cohorts are added
)

classes<- c("Freshman", "Sophomore", "Junior", "Senior")

noco<- "no cohort"

vnm_pl<- c(
  "full_place",
  "incl",
  "n_b",
  "n_db",
  "perc_click_b",
  "perc_click_db",
  "perc_stud_b",
  "perc_stud_db"
)

#function for interactive datatables
reactable_fun<- function() {
  options(
    reactable.theme = reactableTheme(
      color = "hsl(233, 9%, 87%)",
      backgroundColor = "hsl(233, 9%, 19%)",
      borderColor = "hsl(233, 9%, 22%)",
      stripedColor = "hsl(233, 12%, 22%)",
      highlightColor = "hsl(233, 12%, 24%)",
      inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
      selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
      pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
      pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
    )
  )
  rt<- bind_rows(
    pl_cam %>%
      left_join(
        .,
        places %>%
          filter(level == "campus") %>%
          select(full_place, agg_place),
        by = "full_place"
      ) %>%
      distinct(full_place, .keep_all = T) %>%
      mutate(
        incl = incl / 100,
        across(
          perc_click_b:perc_stud_db, ~.x / 100
        )
      ) %>%
      within(
        full_place[
          full_place == "Jordan Schnitzer Museum of Art"
        ]<- "J. Schnitzer Museum of Art"
      ) %>%
      within(
        full_place[
          full_place == "Thompson's University Center"
        ]<- "Thompson's Univ Center"
      ) %>%
      within(
        full_place[
          full_place == "Museum of Natural and Cultural History"
        ]<- "Museum of Nat & Cult Hist"
      ) %>%
      within(
        full_place[
          full_place == "Campus Planning and Facilities Management"
        ]<- "Campus Plan & Facil Mgmt"
      ) %>%
      within(
        agg_place[
          agg_place == "Jordan Schnitzer Museum of Art"
        ]<- "J. Schnitzer Museum of Art"
      ) %>%
      within(
        agg_place[
          agg_place == "Museum of Natural and Cultural History"
        ]<- "Museum of Nat & Cult Hist"
      ) %>%
      within(
        agg_place[
          agg_place == "Campus Planning and Facilities Management"
        ]<- "Campus Plan & Facil Mgmt"
      ) %>%
      within(
        agg_place[
          agg_place == "Student Recreation Complex"
        ]<- "Student Rec Complex"
      ) %>%
      within(
        agg_place[
          agg_place == "Thompson's University Center"
        ]<- "Thompson's Univ Center"
      ) %>%
      within(
        agg_place[
          is.na(agg_place)
        ]<- "Other/Out of Bounds"
      ),
    pl_emu %>%
      left_join(
        .,
        places %>%
          filter(level == "emu") %>%
          select(full_place, agg_place),
        by = "full_place"
      ) %>%
      distinct(full_place, .keep_all = T) %>%
      mutate(
        incl = incl / 100,
        across(
          perc_click_b:perc_stud_db, ~.x / 100
        ),
        agg_place = "EMU-Specific Places"
      ) %>%
      within(
        full_place[
          full_place == "ASUO Student Governance Center"
        ]<- "ASUO Stdnt Gov Cntr"
      ) %>%
      within(
        full_place[
          full_place == "Bartolotti's Pizza Bistro"
        ]<- "Bartolotti's Pizza"
      ) %>%
      within(
        full_place[
          full_place == "Center for Student Involvement Resource Center"
        ]<- "CSI Resource Center"
      ) %>%
      within(
        full_place[
          full_place == "Collegiate Recover Center"
        ]<- "Collegiate Recovery Cntr"
      ) %>%
      within(
        full_place[
          full_place == "Falling Sky Pizzeria and Public House"
        ]<- "Falling Sky"
      ) %>%
      within(
        full_place[
          full_place == "Fraternity and Sorority Life"
        ]<- "Fraternity & Sorority Life"
      ) %>%
      within(
        full_place[
          full_place == "International Student Association"
        ]<- "Intl Stdnt Assoc"
      ) %>%
      within(
        full_place[
          full_place == "International Student Groups"
        ]<- "Intl Stdnt Groups"
      ) %>%
      within(
        full_place[
          full_place == "Legal Services Student Advocacy"
        ]<- "Legal Srvc Stdnt Advocacy"
      ) %>%
      within(
        full_place[
          full_place == "Nontraditional Student Union"
        ]<- "Nontrad Stdnt Union"
      ) %>%
      within(
        full_place[
          full_place == "Scheduling and Event Services"
        ]<- "Sched & Event Services"
      ) %>%
      within(
        full_place[
          full_place == "Student Sustainability Center"
        ]<- "Stdnt Sustainability Cntr"
      )
  ) %>%
    reactable(
      .,
      groupBy = "agg_place",
      showPageSizeOptions = T,
      paginateSubRows = T,
      defaultSorted = c("agg_place", "full_place"),
      sortable = T,
      showSortable = T,
      striped = T,
      highlight = T,
      bordered = T,
      defaultColDef = colDef(
        vAlign = "center",
        headerVAlign = "bottom"
      ),
      columns = list(
        agg_place = colDef(
          name = "Aggregated Place",
          filterable = T,
          align = "left",
          minWidth = 240
        ),
        full_place = colDef(
          name = "Place",
          align = "left",
          minWidth = 215
        ),
        n_b = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(separators = T, digits = 0),
          html = T,
          header = JS(
            'function(column) {
              return `<div style="font-style: italic">n</div>` + "Belong"
            }'
          )
        ),
        n_db = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(separators = T, digits = 0),
          html = T,
          header = JS(
            'function(column) {
              return `<div style="font-style: italic">n</div>` + "Don\'t" +
              "<br>Belong"
            }'
          )
        ),
        perc_click_b = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(percent = T, digits = 1),
          html = T,
          header = JS(
            'function(column) {
              return "Click" + "<br>Belong"
            }'
          )
        ),
        perc_click_db = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(percent = T, digits = 1),
          html = T,
          header = JS(
            'function(column) {
              return "Click" + "<br>Don\'t" + "<br>Belong"
            }'
          )
        ),
        perc_stud_b = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(percent = T, digits = 1),
          html = T,
          header = JS(
            'function(column) {
              return "Student" + "<br>Belong"
            }'
          )
        ),
        perc_stud_db = colDef(
          aggregate = "sum",
          align = "center",
          format = colFormat(percent = T, digits = 1),
          html = T,
          header = JS(
            'function(column) {
              return "Student" + "<br>Don\'t" + "<br>Belong"
            }'
          )
        ),
        incl = colDef(
          aggregate = "mean",
          name = "Inclusive",
          align = "center",
          format = colFormat(percent = T, digits = 1)
        )
      )
    )
  return(rt)
}

```


### For UI piece:
```{r eval=FALSE, include=FALSE}
# this will be in the dashboardbody piece
tabItem(tabName = "table", 
                    
                        # summary section
                        # includeMarkdown("www/summary.md"),    
                        fluidRow(
                            column(3, uiOutput("dynamicFilter")),
                            column(3, reactableOutput("table")) %>% withSpinner(color = "navy")))
```

### For Server piece:
```{r}
#need some of these but not all I think
library(shiny)
library(tidyverse)
library(rvest)
library(leaflet.extras)
library(reactable)

shinyServer(function(input, output) {
    
    # Dynamic UI for additional filters
    output$dynamicFilter <- renderUI({
        if(input$typeSelect == "Undergraduate") {
            selectInput("yearSelect", "Select Year:", 
                        choices = c("2018", "2019", "2020", "2022", "Overall"))
        } else if(input$typeSelect == "International") {
            selectInput("intSelect", "Select Category:", 
                        choices = c("Overall", "Undergrad and Grad 2022", "Undergrad 2020"))
        } else {
            return()
        }
    })

    
    # Render the correct table based on the input selection
    output$table <- renderReactable({
        if(input$typeSelect == "Undergraduate" && input$yearSelect == "Overall") {
            rt_cam_us_ug
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2022") {
            rt_cam_us_ug_ay2122
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2020") {
            rt_cam_us_ug_ay1920
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2019") {
            rt_cam_us_ug_ay1819
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2018") {
            rt_cam_us_ug_ay1718
        } else if(input$typeSelect == "International" && input$intSelect == "Overall") {
            rt_cam_i
        } else if(input$typeSelect == "International" && input$intSelect == "Undergrad and Grad 2022") {
            rt_cam_i_ay2122
        } else if(input$typeSelect == "International" && input$intSelect == "Undergrad 2020") {
            rt_cam_i_ug_ay1920
        } else if(input$typeSelect == "Graduate") {
            rt_cam_gr_ay2122
        }
    })
    
})
```

