---
title: "Where?"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What we need here:

- tables under "Where?" tab
- omit heatmaps (these are in their own section)
- campus inclusiveness treemap
- emu inclusiveness treemap

## Brian's Code
```{r}

```

## Standardize
```{r}

```


## UI draft

## Server draft


## Possibly useful code


just droppped in some code below. this is just the outline and works when you load everything in as .RData, but we want to avoid that. but you can use as draft - anwesha

For UI piece:
```{r eval=FALSE, include=FALSE}
# this will be in the dashboardbody piece
tabItem(tabName = "table", 
                    
                        # summary section
                        # includeMarkdown("www/summary.md"),    
                        fluidRow(
                            column(3, uiOutput("dynamicFilter")),
                            column(3, reactableOutput("table")) %>% withSpinner(color = "navy")))
```

For Server piece:
```{r}
#need some of these but not all I think
library(shiny)
library(tidyverse)
library(rvest)
library(leaflet.extras)
library(reactable)

shinyServer(function(input, output) {
    
    # Dynamic UI for additional filters
    output$dynamicFilter <- renderUI({
        if(input$typeSelect == "Undergraduate") {
            selectInput("yearSelect", "Select Year:", 
                        choices = c("2018", "2019", "2020", "2022", "Overall"))
        } else if(input$typeSelect == "International") {
            selectInput("intSelect", "Select Category:", 
                        choices = c("Overall", "Undergrad and Grad 2022", "Undergrad 2020"))
        } else {
            return()
        }
    })

    
    # Render the correct table based on the input selection
    output$table <- renderReactable({
        if(input$typeSelect == "Undergraduate" && input$yearSelect == "Overall") {
            rt_cam_us_ug
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2022") {
            rt_cam_us_ug_ay2122
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2020") {
            rt_cam_us_ug_ay1920
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2019") {
            rt_cam_us_ug_ay1819
        } else if(input$typeSelect == "Undergraduate" && input$yearSelect == "2018") {
            rt_cam_us_ug_ay1718
        } else if(input$typeSelect == "International" && input$intSelect == "Overall") {
            rt_cam_i
        } else if(input$typeSelect == "International" && input$intSelect == "Undergrad and Grad 2022") {
            rt_cam_i_ay2122
        } else if(input$typeSelect == "International" && input$intSelect == "Undergrad 2020") {
            rt_cam_i_ug_ay1920
        } else if(input$typeSelect == "Graduate") {
            rt_cam_gr_ay2122
        }
    })
    
})
```

